Optimizing and Incrementalizing Collection Queries by AST Transformations

### 2017-07-25 aosd13/Evaluation.tex
Reformat code in Ch. 5 for wider column
Automated search and replace of Sec.~\ref with \cref

	\item[(1)] \textbf{Modularized Scala implementation:} 
	We reimplemented each query as an expression on Scala collections\--- our baseline implementation. For modularity, we separated reusable domain abstractions into subqueries. We confirmed the abstractions with a domain expert and will later illustrate them to emphasize their general nature.
	\item[(2)] \textbf{Hand-optimized Scala implementation:} Next, we asked a domain expert to performed manual optimizations on the modularized queries. The expert should perform optimizations, such as inlining and filter hoisting, where he could find performance improvements.
%Specifically, we inlined all subqueries into a single query and performed the following optimization: loop fusion, \chk{...}.
	\item[(3)] \textbf{\LoS\ implementation:} Finally, we rewrote the modularized Scala queries from (1) as \LoS\ queries. The rewrites are of purely syntactic nature to use our library (as described in Sec.~\ref{subsec:adaptingaquery}) and preserve the modularity of the queries.
\end{enumerate}

Since \LoS\ supports executing queries with and without optimizations and indexes, we measured actually three different execution modes of the \LoS\ implementation:
\begin{enumerate}
	\item[($3^-$)] \textbf{\LoS\ without optimizer:} First, we execute the \LoS\ queries without performing optimization first, which should show the \LoS{} overhead compared to the modular Scala implementation (1).
However, common-subexpression elimination is still used here, since it is part of the compilation pipeline. This is appropriate to counter the effects of excessive inlining due to using a deep embedding, as explained in Sec.~\ref{sec:representation}.
	\item[($3^o$)] \textbf{\LoS\ with optimizer:} Next, we execute \LoS\ queries after optimization.
	\item[($3^x$)] \textbf{\LoS\ with optimizer and indexes:} Finally, we execute the queries after providing a set of indexes that the optimizer can consider.
	%The measured times include the time for optimization, but not the time for creating the indexes (see discussion below).
\end{enumerate}

@@

%reimplementation
We implemented each query three times (see implementations (1)--(3) in Sec.~\ref{sec:implemenationsandspeedups}) following the specifications given in the FindBugs documentation (0). Instead of using a hierarchy of visitors as the original implementations of the queries in FindBugs, we wrote the queries as for-comprehensions in Scala on an in-memory representation created by the Scala toolkit BAT\@.\footnote{\url{http://github.com/Delors/BAT}}
BAT in particular provides comprehensive support for 
writing queries against Java bytecode in an idiomatic way.
We exemplify an analysis in \cref{fig:covariant-equals}: It detects all co-variant \code{equals} methods in a project by iterating over all class files (line 2) and all methods, searching for methods named ``\code{equals}'' that return a boolean value and define a single parameter of the type of the current class.

>>>>

	\item[(1)] \textbf{Modularized Scala implementation:} 
	We reimplemented each query as an expression on Scala collections\--- our baseline implementation. For modularity, we separated reusable domain abstractions into subqueries. We confirmed the abstractions with a domain expert and will later illustrate them to emphasize their general nature.
	\item[(2)] \textbf{Hand-optimized Scala implementation:} Next, we asked a domain expert to performed manual optimizations on the modularized queries. The expert should perform optimizations, such as inlining and filter hoisting, where he could find performance improvements.
%Specifically, we inlined all subqueries into a single query and performed the following optimization: loop fusion, \chk{...}.
	\item[(3)] \textbf{\LoS\ implementation:} Finally, we rewrote the modularized Scala queries from (1) as \LoS\ queries. The rewrites are of purely syntactic nature to use our library (as described in \cref{subsec:adaptingaquery}) and preserve the modularity of the queries.
\end{enumerate}

Since \LoS\ supports executing queries with and without optimizations and indexes, we measured actually three different execution modes of the \LoS\ implementation:
\begin{enumerate}
	\item[($3^-$)] \textbf{\LoS\ without optimizer:} First, we execute the \LoS\ queries without performing optimization first, which should show the \LoS{} overhead compared to the modular Scala implementation (1).
However, common-subexpression elimination is still used here, since it is part of the compilation pipeline. This is appropriate to counter the effects of excessive inlining due to using a deep embedding, as explained in \cref{sec:representation}.
	\item[($3^o$)] \textbf{\LoS\ with optimizer:} Next, we execute \LoS\ queries after optimization.
	\item[($3^x$)] \textbf{\LoS\ with optimizer and indexes:} Finally, we execute the queries after providing a set of indexes that the optimizer can consider.
	%The measured times include the time for optimization, but not the time for creating the indexes (see discussion below).
\end{enumerate}

@@

%reimplementation
We implemented each query three times (see implementations (1)--(3) in \cref{sec:implemenationsandspeedups}) following the specifications given in the FindBugs documentation (0). Instead of using a hierarchy of visitors as the original implementations of the queries in FindBugs, we wrote the queries as for-comprehensions in Scala on an in-memory representation created by the Scala toolkit BAT\@.\footnote{\url{http://github.com/Delors/BAT}}
BAT in particular provides comprehensive support for 
writing queries against Java bytecode in an idiomatic way.
We exemplify an analysis in \cref{fig:covariant-equals}: It detects all co-variant \code{equals} methods in a project by iterating over all class files (line 2) and all methods, searching for methods named ``\code{equals}'' that return a boolean value and define a single parameter of the type of the current class.

### 2017-07-25 aosd13/graphs/queryTables.tex
Revisions from Klaus on AOSD13 text
Ch.6: Improve placement specifiers for tables
Automated search and replace of Sec.~\ref with \cref

\begin{table}
\begin{tabular}{p{7cm}r}\toprule
Abstraction & Used \\ \midrule
% calculate class hierarchy & 5 \\
All fields in all class files	& 4\\
All methods in all class files	& 3\\
All method bodies in all class files	& 3\\
All instructions in all method bodies and their bytecode index	& 5\\
Sliding window (size $n$) over all instructions (and their index) &	3\\
\bottomrule
\end{tabular}\\
\nocaptionrule\caption{Description of abstractions removed during hand-optimization and number of queries where the abstraction is used (and optimized away).}
\label{table:implemented-abstractions}
\end{table}

\newcommand{\captionEvalTable}{%
As in in Sec.~\ref{sec:implemenationsandspeedups}, (1) denotes the modular Scala
implementation, (2) the hand-optimized Scala one, and ($3^-$), ($3^o$), ($3^x$)
refer to the {\LoS} implementation when run, respectively, without
optimizations, with optimizations, with optimizations and indexing.
Queries marked with the $R$ superscript were selected by random sampling.}
\newcommand{\tablerowsize}{\scriptsize}
\begin{table*}[tb]
\centering
\input{\graphPath{EvalTable}}
\nocaptionrule\caption{Performance results. \captionEvalTable}
\label{table:performance}
\end{table*}

\begin{table*}[tb]
\centering
\input{\graphPath{EvalSummaryTable}}
\nocaptionrule\caption{Average performance ratios.
This table summarizes all interesting performance ratios across all queries,
using the geometric mean~\citep{Fleming86}.
The meaning of speedups is discussed in Sec.~\ref{sec:implemenationsandspeedups}.}
\label{table:performanceAvg}
\end{table*}

>>>>

\newcommand{\captionEvalTable}{%
As in in \cref{sec:implemenationsandspeedups}, (1) denotes the modular Scala
implementation, (2) the hand-optimized Scala one, and ($3^-$), ($3^o$), ($3^x$)
refer to the {\LoS} implementation when run, respectively, without
optimizations, with optimizations, with optimizations and indexing.
Queries marked with the $R$ superscript were selected by random sampling.}
\newcommand{\tablerowsize}{\scriptsize}
\begin{sidewaystable}[ph!]
\centering
\input{\graphPath{EvalTable}}
\nocaptionrule\caption{Performance results. \captionEvalTable}
\label{table:performance}
\end{sidewaystable}

\begin{table}[h]
  \centering
  \footnotesize
\input{\graphPath{EvalSummaryTable}}
\nocaptionrule\caption{Average performance ratios.
This table summarizes all interesting performance ratios across all queries,
using the geometric mean~\citep{Fleming86}.
The meaning of speedups is discussed in \cref{sec:implemenationsandspeedups}.}
\label{table:performanceAvg}
\end{table}

\begin{table}[h!]
\begin{tabular}{p{7cm}r}\toprule
Abstraction & Used \\ \midrule
% calculate class hierarchy & 5 \\
All fields in all class files	& 4\\
All methods in all class files	& 3\\
All method bodies in all class files	& 3\\
All instructions in all method bodies and their bytecode index	& 5\\
Sliding window (size $n$) over all instructions (and their index) &	3\\
\bottomrule
\end{tabular}\\
\nocaptionrule\caption{Description of abstractions removed during hand-optimization and number of queries where the abstraction is used (and optimized away).}
\label{table:implemented-abstractions}
\end{table}

### 2017-07-25 aosd13/paperBody.tex
Fix thinko: Input, don't include evalResLos
Move \part commands to included files to work around LaTeX bug
The resolving hint came from
https://tex.stackexchange.com/questions/18253/force-addtocontents-to-be-placed-in-the-correct-order#comment34261_18254
and https://tex.stackexchange.com/a/10297/1340.
Point out these are contributions for a part
Automated search and replace of Sec.~\ref with \cref

@@

Overall, our main contributions are the following:
\begin{itemize}
\item We illustrate the tradeoff between modularity and performance when manipulating collections, caused by the lack of domain-specific optimizations~(Sec.~\ref{sec:motivation}). Conversely, we illustrate how domain-specific optimizations lead to more readable and more modular code (Sec.~\ref{sec:solution}).
\item We present the design and implementation of \LoS, an embedded DSL for queries on collections in Scala (Sec.~\ref{sec:implementation}).
%\LoS\ makes heavy usage of advanced Scala features to preserve the ``look and feel'' of native Scala queries
% and is hence a significant showcase for these features~(Sec.~\ref{sec:implementation}).
 \item We evaluate \LoS\ to show that it supports writing queries that are at the same time modular and fast. We do so by re-implementing several code analyses of the FindBugs tool.
 The resulting code is more modular and/or more efficient, in some cases by orders of magnitude.
 In these case studies, we measured average speedups of \avgSpeedupT{} with a maximum of \maxSpeedupT{}~(Sec.~\ref{sec:evaluation}).
\end{itemize}

@@

In general, one can only resolve these inefficiencies by manually optimizing the query; however, we will observe that these manual optimizations produce less modular code.%
\footnote{%
The existing Scala collections API supports optimization, for instance through non-strict variants of the query operators (called `views' in Scala), but they can only
be used for a limited set of optimizations, as we discuss in Sec.~\ref{sec:relwork}.}

@@

There have been many approaches for a closer integration of SQL queries into programs, such as
HaskellDB~\citep{Leijen99DSEC} (which also inspired \LINQ), or Ferry~\citep{Grust:2009:FDP:1559845.1559982} 
(which moves part of a program execution to a database). In Scala, there are also
APIs which integrate SQL queries more closely such as
Slick.\footnote{\url{http://slick.typesafe.com/}} Its frontend allows to define
and combine type-safe queries, similarly to ours (also in the way it is
implemented).
However, the language for defining queries maps to SQL, so it does not support nesting collections
in other collections (a feature which simplified our example in
Sec.~\ref{sec:motivation}), nor distinguishes statically between different kinds of
collections, such as \code{Set} or \code{Seq}.
Based on Ferry, ScalaQL~\citep{JOT:issue_2010_07/article3} extends Scala with a compiler-plugin to integrate a query language on top of a relational database. The work by \citet{Spiewak09scalaql:language-integrated} is
 unrelated to~\citep{JOT:issue_2010_07/article3} but also called ScalaQL\@. It is similar to our approach in that it also 
proposes to reify queries based on for-comprehensions, but it is not clear from their paper how the reification
works.\footnote{We contacted the authors; they were not willing to provide more details or the sources of their approach.}

@@

Scala collections also provide \emph{views}, which are closer to {\LoS}. Unlike
standard query operators, they create \emph{lazy} collections. Like {\LoS},
views reify query operators as data structures and interpret them later. Unlike
{\LoS}, views are not used for automatic query optimization, but for explicitly
changing the evaluation order of collection processing.
%
Moreover, they cannot be reused by {\LoS} as they reify too little: Views embed
deeply only the outermost pipeline of collection operators, while they embed
shallowly nested collection operators and other Scala code in queries, such as
arguments of \code{filter}, \code{map} and \code{flatMap}.
%
Deep embedding of the whole query is necessary for many optimizations, as
discussed in Sec.~\ref{sec:solution}.

>>>>

\input{aosd13/graphs/evalResLos}

\part{Optimizing Collection Queries by Reification}
\label{part:ch-aosd13}

@@

Overall, our main contributions in \cref{part:ch-aosd13} are the following:
\begin{itemize}
\item We illustrate the tradeoff between modularity and performance when manipulating collections, caused by the lack of domain-specific optimizations~(\cref{sec:motivation}). Conversely, we illustrate how domain-specific optimizations lead to more readable and more modular code (\cref{sec:solution}).
\item We present the design and implementation of \LoS, an embedded DSL for queries on collections in Scala (\cref{sec:implementation}).
%\LoS\ makes heavy usage of advanced Scala features to preserve the ``look and feel'' of native Scala queries
% and is hence a significant showcase for these features~(\cref{sec:implementation}).
 \item We evaluate \LoS\ to show that it supports writing queries that are at the same time modular and fast. We do so by re-implementing several code analyses of the FindBugs tool.
 The resulting code is more modular and/or more efficient, in some cases by orders of magnitude.
 In these case studies, we measured average speedups of \avgSpeedupT{} with a maximum of \maxSpeedupT{}~(\cref{sec:evaluation}).
\end{itemize}

@@

In general, one can only resolve these inefficiencies by manually optimizing the query; however, we will observe that these manual optimizations produce less modular code.%
\footnote{%
The existing Scala collections API supports optimization, for instance through non-strict variants of the query operators (called `views' in Scala), but they can only
be used for a limited set of optimizations, as we discuss in \cref{sec:relwork}.}

@@

There have been many approaches for a closer integration of SQL queries into programs, such as
HaskellDB~\citep{Leijen99DSEC} (which also inspired \LINQ), or Ferry~\citep{Grust:2009:FDP:1559845.1559982} 
(which moves part of a program execution to a database). In Scala, there are also
APIs which integrate SQL queries more closely such as
Slick.\footnote{\url{http://slick.typesafe.com/}} Its frontend allows to define
and combine type-safe queries, similarly to ours (also in the way it is
implemented).
However, the language for defining queries maps to SQL, so it does not support nesting collections
in other collections (a feature which simplified our example in
\cref{sec:motivation}), nor distinguishes statically between different kinds of
collections, such as \code{Set} or \code{Seq}.
Based on Ferry, ScalaQL~\citep{JOT:issue_2010_07/article3} extends Scala with a compiler-plugin to integrate a query language on top of a relational database. The work by \citet{Spiewak09scalaql:language-integrated} is
 unrelated to~\citep{JOT:issue_2010_07/article3} but also called ScalaQL\@. It is similar to our approach in that it also 
proposes to reify queries based on for-comprehensions, but it is not clear from their paper how the reification
works.\footnote{We contacted the authors; they were not willing to provide more details or the sources of their approach.}

@@

Scala collections also provide \emph{views}, which are closer to {\LoS}. Unlike
standard query operators, they create \emph{lazy} collections. Like {\LoS},
views reify query operators as data structures and interpret them later. Unlike
{\LoS}, views are not used for automatic query optimization, but for explicitly
changing the evaluation order of collection processing.
%
Moreover, they cannot be reused by {\LoS} as they reify too little: Views embed
deeply only the outermost pipeline of collection operators, while they embed
shallowly nested collection operators and other Scala code in queries, such as
arguments of \code{filter}, \code{map} and \code{flatMap}.
%
Deep embedding of the whole query is necessary for many optimizations, as
discussed in \cref{sec:solution}.

### 2017-07-25 aosd13/pepm13/caseStudyImpl.tex
Automated search and replace of Sec.~\ref with \cref

%\section{The EDSL interface: embedding Scala expressions}
% Scala-virtualized has no polymorphic lift, unlike us.
% 2. Embedding collections into Scala
% When does one need asSquopt?
To optimize a query as described in the previous section, {\LoS} needs to reify, optimize and execute queries. 
Our implementation assigns responsibility for these steps to three main components: A generic library for reification and execution of general Scala expressions, a more specialized library for reification and execution of query operators, and a dedicated query optimizer.
Queries need then to be executed through either compilation (already discussed in
Sec.~\ref{sec:execution}) or interpretation (to discuss in Sec.~\ref{sec:interpretation}).
We describe the implementation in more detail in the rest of this section. The full implementation is also available online\footnote{\url{http://www.informatik.uni-marburg.de/~pgiarrusso/SQuOpt}}.
%\url{https://github.com/Blaisorblade/SQuOpt}.

A core idea of {\LoS} is to reify Scala code as a data structure in memory. A programmer could directly create instances of that data structure, but we also provide a more convenient interface based on advanced Scala features such as implicit conversions and type inference. That interface allows to automatically reify code with a minimum of programmer annotations, as shown in the examples in Sec.~\ref{sec:solution}. Since this is a case study on Scala's support for deep embedding of DSLs, we also describe in this section how Scala supports our task. In particular, we report on techniques we used and issues we faced.

@@

\code{Author} is not part of {\LoS} or the standard Scala library, but an application-specific class, hence {\LoS} cannot
pre-define the necessary lifting code. Instead, the application programmer needs
to provide this code to connect {\LoS} to his application. To support the
application programmer with this tedious task, we provide a code generator which
discovers the interface of a class through reflection on its compiled version
and generates the boilerplate code such as the one above for \code{Author}. It
also generates
the application-specific expression tree types such as \code{AuthorFirstName} as shown in Sec.~\ref{subsec:repexptrees}.
In general, query writers need to generate and import the boilerplate lifting code for all application-specific types they want to use in a {\LoS} query.

@@

Note how \code{map}'s parameter \code{f} has type \code{Exp[T] => Exp[U]} as necessary to enable Scala's syntax for anonymous functions and automatic lifting of the function body. This implementation would work for queries on lists, but does not support other collection types or queries where the collection type changes. We show in Sec.~\ref{subsec:collections} how {\LoS} integrates with such advanced features of the Scala Collection EDSL.

@@

After optimization, {\LoS} needs to interpret the optimized expression trees to perform the query. Therefore, the trait \code{Exp[T]} declares an \code{def interpret(): T} method, and each expression node overrides it appropriately to implement a mostly standard typed, tagless~\citep{carette09finally}, environment-based interpreter. The interpreter computes a value of type \code{T} from an expression tree of type \code{Exp[T]}. This design allows query writers to extend the interpreter to handle application-specific operations. In fact, the lifting generator described in Sec.~\ref{sec:lifting-ho} automatically generates appropriate definitions of \code{interpret} for the lifted operations.

@@

%We show in Sec.~\ref{subsec:transf} how we implement the inverse conversion from FOAS to HOAS in terms of substitution. We can thus choose which representation to use for the task at hand; again in Sec.~\ref{subsec:transf} we show that supporting transformation and efficient interpretation requires internally using a FOAS representation.

>>>>

%\section{The EDSL interface: embedding Scala expressions}
% Scala-virtualized has no polymorphic lift, unlike us.
% 2. Embedding collections into Scala
% When does one need asSquopt?
To optimize a query as described in the previous section, {\LoS} needs to reify, optimize and execute queries. 
Our implementation assigns responsibility for these steps to three main components: A generic library for reification and execution of general Scala expressions, a more specialized library for reification and execution of query operators, and a dedicated query optimizer.
Queries need then to be executed through either compilation (already discussed in
\cref{sec:execution}) or interpretation (to discuss in \cref{sec:interpretation}).
We describe the implementation in more detail in the rest of this section. The full implementation is also available online\footnote{\url{http://www.informatik.uni-marburg.de/~pgiarrusso/SQuOpt}}.
%\url{https://github.com/Blaisorblade/SQuOpt}.

A core idea of {\LoS} is to reify Scala code as a data structure in memory. A programmer could directly create instances of that data structure, but we also provide a more convenient interface based on advanced Scala features such as implicit conversions and type inference. That interface allows to automatically reify code with a minimum of programmer annotations, as shown in the examples in \cref{sec:solution}. Since this is a case study on Scala's support for deep embedding of DSLs, we also describe in this section how Scala supports our task. In particular, we report on techniques we used and issues we faced.

@@

\code{Author} is not part of {\LoS} or the standard Scala library, but an application-specific class, hence {\LoS} cannot
pre-define the necessary lifting code. Instead, the application programmer needs
to provide this code to connect {\LoS} to his application. To support the
application programmer with this tedious task, we provide a code generator which
discovers the interface of a class through reflection on its compiled version
and generates the boilerplate code such as the one above for \code{Author}. It
also generates
the application-specific expression tree types such as \code{AuthorFirstName} as shown in \cref{subsec:repexptrees}.
In general, query writers need to generate and import the boilerplate lifting code for all application-specific types they want to use in a {\LoS} query.

@@

Note how \code{map}'s parameter \code{f} has type \code{Exp[T] => Exp[U]} as necessary to enable Scala's syntax for anonymous functions and automatic lifting of the function body. This implementation would work for queries on lists, but does not support other collection types or queries where the collection type changes. We show in \cref{subsec:collections} how {\LoS} integrates with such advanced features of the Scala Collection EDSL.

@@

After optimization, {\LoS} needs to interpret the optimized expression trees to perform the query. Therefore, the trait \code{Exp[T]} declares an \code{def interpret(): T} method, and each expression node overrides it appropriately to implement a mostly standard typed, tagless~\citep{carette09finally}, environment-based interpreter. The interpreter computes a value of type \code{T} from an expression tree of type \code{Exp[T]}. This design allows query writers to extend the interpreter to handle application-specific operations. In fact, the lifting generator described in \cref{sec:lifting-ho} automatically generates appropriate definitions of \code{interpret} for the lifted operations.

@@

%We show in \cref{subsec:transf} how we implement the inverse conversion from FOAS to HOAS in terms of substitution. We can thus choose which representation to use for the task at hand; again in \cref{subsec:transf} we show that supporting transformation and efficient interpretation requires internally using a FOAS representation.

### 2017-07-25 aosd13/pepm13/caseStudyIntro.tex
Automated search and replace of Sec.~\ref with \cref

\begin{itemize}
\item We illustrate modularity limitations when manipulating collections, caused by the lack of domain-specific optimizations. Conversely, we illustrate how domain-specific optimizations lead to more readable and more modular code~(Sec.~\ref{sec:motivation}).
\item We present the design~(Sec.~\ref{sec:solution}) and implementation~(Sec.~\ref{sec:implementation}) of \LoS, an embedded DSL for queries on collections in Scala.
\item We discuss how Scala supports expressing the interface~(Section~\ref{sec:intfScala}).
%\LoS\ makes heavy usage of advanced Scala features to preserve the ``look and feel'' of native Scala queries
% and is hence a significant showcase for these features~(Sec.~\ref{sec:implementation}).
 \item We evaluate \LoS\ by re-implementing several code analyses of the Findbugs tool~\citep{DBLP:journals/sigplan/HovemeyerP04}.
 The resulting code is shorter and/or more efficient, in some cases by orders of magnitude~(Sec.~\ref{sec:evaluation}).
 \item We discuss the degree to which \LoS\ fulfills our original design goal and extract lessons for
 both future DSL developers and general-purpose language designers. %\chk{none of these abbreviations was introducted.} %DSL was introduced, I avoid GPL
% In particular, we propose areas in which the support of Scala
% for embedding DSLs should be improved~(Sec.~\ref{sec:discussion}).
\end{itemize}

>>>>

\begin{itemize}
\item We illustrate modularity limitations when manipulating collections, caused by the lack of domain-specific optimizations. Conversely, we illustrate how domain-specific optimizations lead to more readable and more modular code~(\cref{sec:motivation}).
\item We present the design~(\cref{sec:solution}) and implementation~(\cref{sec:implementation}) of \LoS, an embedded DSL for queries on collections in Scala.
\item We discuss how Scala supports expressing the interface~(Section~\ref{sec:intfScala}).
%\LoS\ makes heavy usage of advanced Scala features to preserve the ``look and feel'' of native Scala queries
% and is hence a significant showcase for these features~(\cref{sec:implementation}).
 \item We evaluate \LoS\ by re-implementing several code analyses of the Findbugs tool~\citep{DBLP:journals/sigplan/HovemeyerP04}.
 The resulting code is shorter and/or more efficient, in some cases by orders of magnitude~(\cref{sec:evaluation}).
 \item We discuss the degree to which \LoS\ fulfills our original design goal and extract lessons for
 both future DSL developers and general-purpose language designers. %\chk{none of these abbreviations was introducted.} %DSL was introduced, I avoid GPL
% In particular, we propose areas in which the support of Scala
% for embedding DSLs should be improved~(\cref{sec:discussion}).
\end{itemize}
